\documentclass[aspectratio=169,10pt]{beamer}

\usetheme{Madrid}
\usecolortheme{default}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[frame number]

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,calc,shapes.geometric}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

\title[Fairness-Aware Routing]{Fairness-Aware Routing in Quantum Networks \& Clinical Settings}
\subtitle{via Multi-Armed, Contextual, and Informative Bandit Methods}
\author[P. Z. Garcia]{Piter Z. Garcia\\Advisors: Daniel Krutz and Travis Desell}
\institute[RIT]{Rochester Institute of Technology\\DSCI 601 -- Applied Data Science I}
\date{Final Presentation}

\definecolor{ritorange}{RGB}{247,105,2}
\definecolor{deepblue}{RGB}{31,78,121}
\definecolor{softgreen}{RGB}{72,160,98}
\definecolor{softred}{RGB}{190,75,72}
\definecolor{softgray}{RGB}{245,247,250}
\definecolor{softblue}{RGB}{88,137,174}
\definecolor{softpurple}{RGB}{135,99,171}
\definecolor{phase1blue}{RGB}{52,152,219}
\definecolor{phase2green}{RGB}{46,204,113}
\definecolor{phase3orange}{RGB}{230,126,34}
\definecolor{phase4purple}{RGB}{155,89,182}

\setbeamercolor{title}{fg=deepblue}
\setbeamercolor{frametitle}{fg=deepblue}
\setbeamercolor{structure}{fg=ritorange}

\newcommand{\mab}{\textsc{MAB}}
\newcommand{\cmab}{\textsc{CMAB}}
\newcommand{\icmab}{\textsc{iCMAB}}
\newcommand{\sds}{\textsc{SDS}}
\newcommand{\equitas}{\textsc{EQUITAS}}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{15-Minute Presentation Plan}
\begin{enumerate}
    \item Project overview and why it matters.
    \item Updated domain model for clinical and quantum routing.
    \item Approach: four-phase evaluation model and MAB/CMAB/iCMAB comparison.
    \item Updated implementation-aware architecture overview.
    \item Architecture changes and layer details.
    \item GitHub code-review break tied to the architecture.
    \item Demo plan, preliminary results, and next-semester completion.
\end{enumerate}
\end{frame}

\begin{frame}{Project Overview}
\begin{block}{What this project is}
This project studies \textbf{fairness-aware routing under missing context} in two environment families: \textbf{clinical decision support} and \textbf{quantum-network routing}.
\end{block}
\begin{block}{Shared problem}
Both domains are \textbf{sequential decision systems}: they allocate scarce resources under uncertainty, observe only partial feedback, and update future decisions from incomplete evidence.
\end{block}
\textbf{Project goals}
\begin{itemize}
    \item Compare \mab, \cmab, and \icmab{} strategies.
    \item Measure both \textbf{performance} and \textbf{fairness}.
    \item Show how missing or degraded context can create repeated allocation harm.
    \item Build a reproducible framework with reportable artifacts.
\end{itemize}
\end{frame}

\begin{frame}{Why This Project Matters}
\begin{columns}[T]
\begin{column}{0.48\textwidth}
\begin{block}{Clinical impact}
Routing decisions affect real patient outcomes.
\end{block}

\begin{itemize}
    \item Who receives a diagnostic test?
    \item Who gets retested or escalated?
    \item Whose risk is missed because context is incomplete?
\end{itemize}

\vspace{0.4em}

\alert{A policy can look accurate on average while still delaying access to critical resources/care for a vulnerable group.}
\end{column}

\begin{column}{0.48\textwidth}
\begin{block}{Quantum-network impact}
Routing decisions affect service quality under noisy conditions.
\end{block}

\begin{itemize}
    \item Which path gets selected?
    \item Which flows receive scarce qubit or link resources?
    \item Which users experience repeated failure or latency?
\end{itemize}

\vspace{0.4em}

\alert{A policy can maximize total throughput while still giving some flows consistently worse service.}
\end{column}
\end{columns}

\vspace{0.6em}

\begin{block}{Core reason this matters}
Fairness-aware routing asks whether the system is making good decisions
\textbf{for everyone affected}, not only good decisions on average.
\end{block}
\end{frame}

\begin{frame}{Updated Domain Model}
\centering
\resizebox{0.96\textwidth}{!}{%
\begin{tikzpicture}[
  font=\scriptsize,
  phasebox/.style={draw, rounded corners=4pt, align=center,
              text width=1.72cm, minimum height=0.72cm,
              inner sep=3pt, text=white, font=\scriptsize\bfseries},
  phase1/.style={phasebox, fill=phase1blue},
  phase2/.style={phasebox, fill=phase2green},
  phase3/.style={phasebox, fill=phase3orange},
  phase4/.style={phasebox, fill=phase4purple},
  arr/.style={-Stealth, thick, gray!65},
  darr/.style={-Stealth, thick, dashed, gray!55},
  lbl/.style={font=\scriptsize\bfseries, align=center}
]
\fill[phase1blue!12, rounded corners=6pt]   (-0.65,-2.10) rectangle (4.10,2.15);
\fill[phase2green!12, rounded corners=6pt]  (4.30,-2.10) rectangle (7.40,2.15);
\fill[phase3orange!12, rounded corners=6pt] (7.65,-2.10) rectangle (11.90,2.15);
\fill[phase4purple!12, rounded corners=6pt] (12.15,-2.10) rectangle (18.25,2.15);

\node[phase1] (clin) at (0.55,0.62) {Clinical\\Resource Routing};
\node[phase1] (quant) at (0.55,-0.62) {Quantum\\Network Routing};
\node[phase1, double, double distance=1.4pt] (env) at (3.00,0.00) {Environment /\\Testbed};

\node[phase2] (deg) at (5.85,0.72) {Missing / Noisy /\\Delayed Context};
\node[phase2] (ctx) at (5.85,-0.52) {Observed\\Context};

\node[phase3] (pol) at (8.70,0.00) {Policy / Model\\MAB--CMAB--iCMAB};
\node[phase3] (act) at (10.80,0.00) {Routing\\Action};

\node[phase4] (fb)  at (13.05,-0.86) {Partial Feedback\\success / reward};
\node[phase4] (log) at (15.05,0.60) {Utility + Fairness\\Logger};
\node[phase4] (mit) at (17.15,-0.86) {Mitigation +\\Artifacts};

\draw[arr] (clin)--(env);
\draw[arr] (quant)--(env);
\draw[arr] (env)--(ctx);
\draw[arr] (deg)--(ctx);
\draw[arr] (ctx)--(pol);
\draw[arr] (pol)--(act);
\draw[arr] (act)--(fb);
\draw[arr] (act)--(log);
\draw[arr] (fb)--(log);
\draw[arr] (log)--(mit);
\draw[darr] (mit.south) to[bend right=18] (pol.south);

\node[lbl, text=phase1blue]   at (1.75,-1.82) {\textbf{Phase 1}\\Environment};
\node[lbl, text=phase2green]  at (5.85,-1.82) {\textbf{Phase 2}\\Context};
\node[lbl, text=phase3orange] at (9.78,-1.82) {\textbf{Phase 3}\\Decision};
\node[lbl, text=phase4purple] at (15.20,-1.82) {\textbf{Phase 4}\\Evaluation};
\end{tikzpicture}%
}

\vspace{0.45em}
\scriptsize
\begin{tabular}{p{0.22\textwidth}p{0.65\textwidth}}
\toprule
\textbf{Domain element} & \textbf{Current implementation mapping} \\
\midrule
Environment / testbed & \texttt{ClinicalEnvironment} plus preserved quantum-routing testbed path \\
Context observation & site/cohort/service context, missing-context flags, stale/noisy route information \\
Policy / action & \texttt{ClinicalModelRegistry}, \texttt{FairAllocatorV1}, \texttt{ClinicalBanditUCB}, MAB/CMAB/iCMAB routing policies \\
Evaluation / mitigation & partial feedback, \texttt{ClinicalEquitasMediator}, fairness states, summaries, manifests, figures \\
\bottomrule
\end{tabular}

\vspace{0.25em}
\begin{itemize}\scriptsize
  \item The model captures the shared SDS loop: only the chosen action creates observed feedback; unchosen actions remain counterfactual.
  \item Fairness risk appears when context quality is systematically worse for one group, site, cohort, or route class.
\end{itemize}
\end{frame}

\begin{frame}{Why the Domain Model Changed}
\begin{columns}[T]
\begin{column}{0.48\textwidth}
\centering
\textbf{Old domain view}

\vspace{0.3em}
\resizebox{\linewidth}{!}{%
\begin{tikzpicture}[
  node distance=0.42cm,
  smallbox/.style={draw, rounded corners, align=center, minimum width=1.7cm, minimum height=0.55cm, fill=softgray},
  bad/.style={draw, rounded corners, align=center, minimum width=1.7cm, minimum height=0.55cm, fill=softred!18},
  good/.style={draw, rounded corners, align=center, minimum width=1.7cm, minimum height=0.55cm, fill=softgreen!18},
  arr/.style={-{Stealth}, thick}
]
\node[smallbox] (env) {Environment};
\node[bad, right=0.35cm of env] (ctx) {Context};
\node[smallbox, right=0.35cm of ctx] (pol) {Policy};
\node[smallbox, right=0.35cm of pol] (act) {Action};
\node[good, below=0.55cm of act] (out) {Reward + Fairness};
\node[smallbox, left=0.35cm of out] (rep) {Reporting};
\node[bad, left=0.35cm of rep] (harm) {Disparity};

\draw[arr] (env) -- (ctx);
\draw[arr] (ctx) -- (pol);
\draw[arr] (pol) -- (act);
\draw[arr] (act) -- (out);
\draw[arr] (out) -- (rep);
\draw[arr] (rep) -- (harm);
\draw[arr,dashed] (harm.west) to[bend right=35] (pol.south);
\end{tikzpicture}}
\vspace{0.35em}

{\scriptsize Compact pipeline, but some concepts were merged together.}
\end{column}

\begin{column}{0.48\textwidth}
\centering
\textbf{Updated domain view}

\vspace{0.3em}
\resizebox{\linewidth}{!}{%
\begin{tikzpicture}[
  node distance=0.42cm,
  smallbox/.style={draw, rounded corners, align=center, minimum width=1.7cm, minimum height=0.55cm, fill=softgray},
  bad/.style={draw, rounded corners, align=center, minimum width=1.7cm, minimum height=0.55cm, fill=softred!18},
  good/.style={draw, rounded corners, align=center, minimum width=1.7cm, minimum height=0.55cm, fill=softgreen!18},
  orangebox/.style={draw, rounded corners, align=center, minimum width=1.7cm, minimum height=0.55cm, fill=ritorange!18},
  arr/.style={-{Stealth}, thick}
]
\node[smallbox] (env) {Environment};
\node[bad, right=0.35cm of env] (ctx) {Observed Context};
\node[orangebox, right=0.35cm of ctx] (pol) {Policy Family};
\node[smallbox, right=0.35cm of pol] (act) {Routing Action};
\node[good, below=0.55cm of act] (out) {Observed Outcome};
\node[good, left=0.35cm of out] (fair) {Fairness State};
\node[smallbox, left=0.35cm of fair] (rep) {Reporting Artifact};

\draw[arr] (env) -- (ctx);
\draw[arr] (ctx) -- (pol);
\draw[arr] (pol) -- (act);
\draw[arr] (act) -- (out);
\draw[arr] (out) -- (fair);
\draw[arr] (fair) -- (rep);
\draw[arr,dashed] (fair.west) to[bend right=35] (pol.south);
\end{tikzpicture}}
\vspace{0.35em}

{\scriptsize Clearer separation of decision, outcome, fairness audit, and reporting.}
\end{column}
\end{columns}

\vspace{0.6em}
\begin{block}{Why this matters}
\begin{itemize}
    \item The updated model separates \textbf{observed outcome} from \textbf{fairness state}, so fairness is treated as an audit layer rather than being hidden inside reward.
    \item It makes the \textbf{bandit setting} clearer: only the chosen action is observed, while the other actions remain \textbf{counterfactual}.
    \item It also makes the project more reproducible by showing that \textbf{reporting/validation artifacts} are explicit outputs of the framework.
\end{itemize}
\end{block}
\end{frame}

\input{approach_report/approach_slides.tex}

\begin{frame}{Updated Architecture Overview}
\centering
\vspace{-0.35em}
\resizebox{0.98\textwidth}{!}{%
\input{architecture_report/architecture_diagram.tex}
}
\vspace{-0.15em}
\scriptsize
\textbf{Read left to right:} research context and evidence feed controlled runs; clinical and quantum execution paths produce evaluation records; allocation, EQUITAS mediation, and fairness--performance synthesis generate reviewable artifacts.
\end{frame}

\begin{frame}{What Changed in the Current Architecture}
\small
\begin{tabular}{p{0.24\textwidth}p{0.34\textwidth}p{0.32\textwidth}}
\toprule
\textbf{Region} & \textbf{Current implementation} & \textbf{Why it matters} \\
\midrule
Clinical execution path & \texttt{ClinicalEnvironment}, \texttt{ClinicalExperimentRunner}, \texttt{ClinicalExperimentEvaluator} & Clinical work is executable through a runner/evaluator path. \\
Policy/model path & \texttt{ClinicalModelRegistry}: Oracle, ClinicalBaseline, FairAllocatorV1, ClinicalBanditUCB & The deck can discuss actual model families rather than generic policy boxes. \\
Allocation + mediation & \texttt{ClinicalDefaultResourceAllocator} and \texttt{ClinicalEquitasMediator} & Fairness connects to allocation decisions through mediation, not only post-hoc reporting. \\
Quantum path & legacy quantum notebooks, saved states, state-analysis outputs & Existing quantum routing work remains preserved and feeds the same evaluation surface. \\
Artifacts layer & fairness states, summaries, figures, manifests, reports & The architecture produces evidence that can be reviewed, reproduced, and cited. \\
\bottomrule
\end{tabular}
\end{frame}

\begin{frame}{Architecture Layers in Detail}
\small
\begin{tabular}{p{0.22\textwidth}p{0.32\textwidth}p{0.36\textwidth}}
\toprule
\textbf{Layer} & \textbf{Key components} & \textbf{Responsibility} \\
\midrule
Control + validation & RunSpec, seeds, thresholds, smoke checks, merge criteria & control experiments and acceptance evidence \\
Execution & Clinical fixture, ClinicalEnvironment, quantum saved states & create decision settings and produce outcome records \\
Policy + allocation & ClinicalModelRegistry, FairAllocatorV1, ClinicalBanditUCB, allocator & choose routing actions under partial feedback \\
Mediation + synthesis & ClinicalEquitasMediator, fairness states, evaluator summaries & combine utility, fairness, and intervention context \\
Artifacts & figures, reports, manifests, state-analysis outputs & make results reproducible and reviewable \\
\bottomrule
\end{tabular}
\end{frame}

\begin{frame}{Preliminary Framework Results}
\begin{center}
\begin{tabular}{p{0.43\textwidth}p{0.42\textwidth}}
\toprule
Evidence item & Result \\
\midrule
Clinical embedded path & evaluator, runner, environment, allocator, models, and EQUITAS context run end-to-end \\
Clinical fairness smoke & 16 fairness states across four model families \\
Non-oracle efficiency & FairAllocatorV1: 91.23\%; ClinicalBanditUCB: 84.21\%; ClinicalBaseline: 75.09\% oracle efficiency \\
Reporting layer & 21 manifest-linked artifacts and model-stratified summaries \\
Quantum compatibility & legacy quantum path preserved with fairness sidecar artifacts \\
\bottomrule
\end{tabular}
\end{center}
\end{frame}

\begin{frame}{GitHub Code Review Break}
\begin{block}{Show 2--3 classes not used in the midterm}
Open GitHub and connect each class to the architecture diagram.
\end{block}
\small
\begin{tabular}{p{0.34\textwidth}p{0.48\textwidth}}
\toprule
Class / file to show & Architecture connection \\
\midrule
\texttt{ClinicalExperimentEvaluator} & evaluator orchestration, fairness states, artifacts \\
\texttt{ClinicalExperimentRunner} & run execution over seeds, models, and allocations \\
\texttt{ClinicalModelRegistry} & model families: Oracle, baseline, FairAllocatorV1, ClinicalBanditUCB \\
\texttt{equitas\_mediator.py} & mediation layer and fairness audit context \\
\bottomrule
\end{tabular}
\end{frame}

\begin{frame}{Working Demo Plan}
\begin{enumerate}
    \item Run the clinical fairness smoke/demo path.
    \item Show generated fairness states and model-stratified summaries.
    \item Show report artifacts and manifest linkage.
    \item Point to the COVID clinical foundation as the clinical evidence base.
    \item Explain how the quantum legacy path connects to the same fairness--performance layer.
\end{enumerate}
\end{frame}

\begin{frame}{Next Semester: Architecture Completion}
\begin{enumerate}
    \item Convert COVID test allocation and pulse-ox evidence into executable clinical environments.
    \item Complete active iCMAB missingness-aware updates.
    \item Close the loop so EQUITAS/fairness evidence updates future routing decisions.
    \item Add active fairness-adjusted quantum routing policies.
    \item Build a paper-ready validation hub linking claims, experiments, figures, and reproducibility metadata.
\end{enumerate}
\end{frame}

\begin{frame}{Takeaway}
\begin{block}{Main scientific claim}
Context quality is a fairness variable. Missing, ignored, or biased context can turn partial-feedback learning into repeated allocation harm.
\end{block}
\begin{block}{What was built}
A clinical--quantum evaluation framework that compares performance and fairness across the selected MAB spectrum while preserving reproducible artifacts.
\end{block}
\end{frame}

\begin{frame}{Selected References}
\scriptsize
\begin{itemize}
\item Sjoding et al. Racial bias in pulse oximetry measurement. \textit{New England Journal of Medicine}, 2020.
\item Fawzy et al. Pulse oximetry inaccuracy and delayed COVID treatment eligibility. \textit{JAMA Internal Medicine}, 2022.
\item Fawzy et al. Racial and ethnic discrepancy in pulse oximetry. \textit{JAMA Network Open}, 2023.
\item CDC/NCHS. COVID-19 provisional counts and health disparities.
\item DSCI601 workspace and project architecture materials.
\end{itemize}
\end{frame}

\end{document}
